Maintenance planning on French military aircraft operations

### 2018-09-19 R/presentations/CLAIO_presentation/presentation.Rmd
changes to simplify model in ppt

Reduction to the 'Fixed interval scheduling' in @Smet2015.

@@

## Model: minimum assignment times

\begin{align}
    & a^s_{jti} \geq a_{jti} - a_{j(t-1)i}
            & t =1, ..., \mathcal{T}, j \in \mathcal{J}_t, i \in \mathcal{I}_j \label{eq:start1} \\
    & a^s_{j0i} \geq a_{j0i} - 1 \!1_{i \in \mathcal{A}^{init}_{j}}
            & j \in \mathcal{J}_0, i \in \mathcal{I}_j \label{eq:start2} \\        
    & \sum_{t' \in \mathcal{T}^{MT}_{jt}} a^s_{jt'i} \leq a_{jti} 
    & j \in \mathcal{J}, t \in \mathcal{T}_j, i \in \mathcal{I}_j \label{eq:start3}
\end{align}

Each task needs a minimum continuous duration at each assignment.

@@

## Model: flow constraints

@@

## Model: availability

\begin{align}
   & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}_k} m_{it'} + N^{clust}_{kt} \leq A^{clust}_{kt}
    &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:avalaibility-cluster} \\
   & \sum_{i \in \mathcal{I}_k} rut_{it} \geq H^{clust}_{kt}
    &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:avalaibility-hours-cluster}
\end{align}

Each cluster of aircraft needs a minimum level of availability in number and usage hours.

<!-- # Results -->

<!-- ## Experiments -->

<!-- Instances have been created with the following characteristics: -->

@@

<!-- * 60 - 200 resources. -->
<!-- * 90 periods. -->
<!-- * Tasks: 3 - 9  -->
<!--     * 12 - 36 periods long -->
<!--     * 2 - 5 resources needed -->

>>>>

Reduction to the 'Fixed interval scheduling' in @Smet2015 **proves NP-completeness**.

@@

<!-- ## Model: minimum assignment times -->

<!-- <!-- <div class="incremental"> -->

<!-- \begin{align} -->
<!--     & a^s_{jti} \geq a_{jti} - a_{j(t-1)i} -->
<!--             & t =1, ..., \mathcal{T}, j \in \mathcal{J}_t, i \in \mathcal{I}_j \label{eq:start1} \\ -->
<!--     & a^s_{j0i} \geq a_{j0i} - 1 \!1_{i \in \mathcal{A}^{init}_{j}} -->
<!--             & j \in \mathcal{J}_0, i \in \mathcal{I}_j \label{eq:start2} \\         -->
<!--     & \sum_{t' \in \mathcal{T}^{MT}_{jt}} a^s_{jt'i} \leq a_{jti}  -->
<!--     & j \in \mathcal{J}, t \in \mathcal{T}_j, i \in \mathcal{I}_j \label{eq:start3} -->
<!-- \end{align} -->

<!-- Each task needs a minimum continuous duration at each assignment. -->

@@

## Model: time consumption

@@

## Model: other constraints

* Cluster availability.
* Minimum duration for task assignment.

<!-- ## Model: availability -->

<!-- \begin{align} -->
<!--    & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}_k} m_{it'} + N^{clust}_{kt} \leq A^{clust}_{kt} -->
<!--     &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:avalaibility-cluster} \\ -->
<!--    & \sum_{i \in \mathcal{I}_k} rut_{it} \geq H^{clust}_{kt} -->
<!--     &k \in \mathcal{K}, t \in \mathcal{T} \label{eq:avalaibility-hours-cluster} -->
<!-- \end{align} -->

<!-- Each cluster of aircraft needs a minimum level of availability in number and usage hours. -->

# Results

## Experiments

Instances have been created with the following characteristics:

@@

* 60 - 200 resources.
* 90 periods.
* Tasks: 3 - 9
    * 12 - 36 periods long
    * 2 - 5 resources needed
